Pleiades: Interactive Composing Tools for Vega-Lite Charts

### 2019-06-12 final/paper/paper.tex
Add results

@@

result here

>>>>

One more results that we found was, having the ability to perform the four operations: 
Layer, Concat, Facet and Repeat, it gave user a better understanding of these 
operations and how to properly use then. The validation steps, along with the 
error message that Pleiades provides helps user to understand what they are doing 
wrong, helping them in their education about visualization in general.

In terms of exploring data, the time take to compose different charts and see 
find useful results, went down by a lot because of the high-level of interactivity 
provided. Users don’t have to worry about updating JSON code for ever 
small change in their chart.

Overall, Pleiades resulted in easing beginners to develop composite charts,
save time for users, ease data-exploration, and act as a support toolkit for education.

@@

The key result for Pleiades was how easy it became to compose graph. During our presentation, 
we asked a lot of our peers to try out the our application and compare their workflow to that 
when they used the Vega-Lite API along with a JSON spec. The results were as we expected: 
Pleiades gives a better understanding and ease at composing different charts and see what fits the best.
The key-idea behind why Pleiades makes composing charts easier and more intuitive is because the 
process is bottom-up, whereas Vega-lite is top-down. Also, the graphical user interface provided 
used with a smother way to compose charts, than to write nested JSON specs.
